### 2008-03-17 SAiP/Module1/H3/doc/qualityattributes.tex
Finishing question 2 (at least sort of :-( )

Defining an architectures requirements is not like defining the functional requirements; actually many software professionals believe that they are indeed orthogonal. This is supported by the fact that a set of functional requirements may be implemented by a number of different architectures.

@@

Naturally in order for the scenarios to be able to be used to clarify the architecture it must be possible quantify them, and place them in different categories. This requires that the above scenario(s) are extended with e.g. response time, how many times the user should be able to perform an operation before experiencing a fault (down-town).

@@

\fixme{Insert table with quality attribute breakdown}

As it may be seen, the scenario(s) focus primarily on \emph{Availability} (how rare should it be that a user experience non-resonsiveness and how many simultanious users can the system support), \emph{Usability} (how easy should it be for the user to cancel a transaction halfway through and how easy should it be to pick up a previous transaction), \emph{Performance} (how big a delay can the user expect when performing an operation like a lookup in the database), \emph{Security} (how to avoid someone using stolen credit cards and also prevent a "hacker" from stealing the credit card information either durig the transaction or from the Beer Web Store's database.

@@

The scenarios may be further clarified in order to include the aspects of availability and performance, as shown in tables \ref{tab:availability} and \ref{tab:performance} below:

@@

\fixme{Answer question 3.2}

>>>>

Defining requirements for an architecture is not like defining the functional requirements; actually many software professionals believe that they are indeed orthogonal. This is supported by the fact that a set of functional requirements may be implemented by a number of different architectures.

@@

Naturally in order for the scenarios to be able to be used to clarify the architecture it must be possible to quantify them, and place them in different categories. This requires that the above scenario(s) are extended with e.g. response time, how many times the user should be able to perform an operation before experiencing a fault (down-time).

@@

As it may be seen, the scenario(s) focus primarily on \emph{Availability} (how rare should it be that a user experience non-resonsiveness and how many simultanious users can the system support), \emph{Usability} (how easy should it be for the user to cancel a transaction halfway through and how easy should it be to pick up a previous transaction), \emph{Performance} (how big a delay can the user expect when performing an operation like a lookup in the database), \emph{Security} (how to avoid someone using stolen credit cards and also prevent a "hacker" from stealing the credit card information either during the transaction or from the Beer Web Store's database.

@@

The following scenarios (table \ref{tab:availability} and \ref{tab:performance}) is a possible outcome of prioritization and clarification of quality attribute scenarios as described above:

@@

In a real life system there will of course be many more scenarios to describe the architectural requirements.
